%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Introduction}
\label{chap:intro}


\section{About OpenBotHandy Project}

The ability to handle various household objects is a key technology for future home robots.
This ability includes object recognition, grasping, navigation, task/motion planning and others with safe manner.
OpenBotHandy project aims to develop those manipulation technologies with worldwide open research groups,
especially for more complicated and closer to the actual use case.
Under the purpose, the project plans to define benchmark scenarios for every year while providing real-time benchmark simulation for virtual test \& competition
and baseline manipulation codes.


\section{Robot Platform}

OpenBotHandy project aims to develop manipulation technology of mobile manipulation robot.
Until 2023, this project will utilize Franka Emika Panda manipulation robot with a two-fingered gripper of BotHandy robot.
After that, we plan to employ Samsung BotHandy (new version to appear) mobile manipulation robot for more general in home benchmark scenarios.

For compatibility, any robot platform utilized for this project should be controlled via ROS2 foxy.
Therefore, robot platform provider should provide ROS2 API, 
while making participants be able to control the robot through the provided ROS2 API.


\section{Project Homepage}

The main github page of this project is \textcolor{blue}{\url{https://github.com/OpenBotHandy}}
with homepage being \textcolor{blue}{\url{https://OpenBotHandy.github.io}}.


\section{Organization}

Organizing committee of this project for 2022 is as follows:
\begin{itemize}
\item
Unkyu Park (Samsung Research, Republic of Korea)
%-----------------------------------
\item
Myungsin Kim (Samsung Research, Republic of Korea)
%-----------------------------------
\item
Jaecheol Sim (Samsung Research, Republic of Korea)
%-----------------------------------
\item
Wonsik Shin (Samsung Research, Republic of Korea)
%-----------------------------------
\item
Jeongmin Choi (Samsung Research, Republic of Korea)
%-----------------------------------
\item
Colin Prepscius (Samsung Research America, United States of America)
%-----------------------------------
\item
Alexix Burns (Samsung Research America, United States of America)
%-----------------------------------
\item
Shubam Agrawal (Samsung Research America, United States of America)
%-----------------------------------
\item
Steven Macenski (Samsung Research America, United States of America)
%-----------------------------------
\end{itemize}
