%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Remarks}
\label{chap:remarks}

\section{Participate Benchmark}

OpenBotHandy project will provide an accessibility in advance to invited participants, and receive feedback before public release.
If you have interest on this project or want to use the simulator and baseline manipulation code in advance,
please register your e-mail on the homepage and we will grant access to the github account.

We plan to open a competition on virtual first before opening a real hardware (HW) competition.
Participants of real HW competition will be carefully selected among applicants due to a limited number of supported robot HW platform.
However, participant of virtual benchmark would have a benefit for participating the real HW competition.
Current roadmap of OpenBotHandy project is as follow:
\begin{itemize}
\item
\textbf{Phase 1 (`22.10 $\sim$ `22.12):}
Announce an open robot manipulation benchmark. Receive applications for invited participants for Phase 2.
%---------------------------------- 
\item
\textbf{Phase 2 (`23.01 $\sim$ `23.05):}
Release beta version of basic manipulation code (Starter-kit) \& simulator to invited participants.
Hold closed competition (virtual) with Phase 2 participants.
%---------------------------------- 
\item
\textbf{Phase 3 (`23.06 $\sim$ `23.11):}
Official release of basic manipulation code (Starter-kit) \& simulator to public.
Hold workshop and competition (virtual) on robotics conference.
\end{itemize}


\section{Contribute to Project}

We look forward to a contribution of open researchers and developers after public release.
Please follow up our project!