%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Tasks and Rules}
\label{chap:task}

\section{General Rules}

The aim of this benchmark is to evaluate robot intelligence for manipulation in a human friendly environment without an aid of an user.
Therefore, a robot should execute each benchmark task autonomously by itself,
including avoiding dangerous behavior for human and object and recovering in emergency status.
More detailed description of individual prerequisite \& rules are as follow:
\begin{itemize}
%------------------
\item
\textbf{Fully automated cycle:}
Once a robot is activated (by person) to start a single test of a task, 
no other external input is allowed until the robot determined that it has completed the test and must return to its end status.
(i.e., need to implement \textit{stop} fucntion which can decide if a single test is finished or not.) 
%------------------
\item
\textbf{No human intervention:}
While a robot is performing a single test no human intervention to test environment) is allowed
(e.g., moving/removing tableware that is before and after operation etc.)
%------------------
\item
\textbf{Fixed start/end status for a task:}
There is a predefined start/end position/orientation of end-effector or joints,
which robot must be placed in before excute a single test and must return to when it complete the test.
\end{itemize}

On the other hands, each task has its own task scenario, success/penalty conditions, and score system 
while common penalties for dangerous behaviors are described in \ref{subsec:penalty}. 

\subsection{Common Penalties}
\label{subsec:penalty}

For a robot working in daily life environment, safety is the utmost imortant.
Therefore, there is a penalty for a robot of intentional/unintentionl dangerous behavior. 
The number of such behavior is counted and weigthed to discount a final score of each single test.
The list of common penalty condition is as follows:
\begin{itemize}
\item
\textbf{Drop}:
Unintentional droping of object during interaction will be counted as drop event.
%---------------
\item
\textbf{Push}:
All object's position should be changed by a robot's operation.
Unintentional position change by e.g., colliding with in any part of a robot will be counted as pused event, 
if its position change is more than 10cm or clearly visible and drastic for refree eyes.
%---------------
\item
\textbf{Knock-down}:
Same for the push event, orientation of all objects except utensil should be changed by a robot's operation.
Unintentional orientation change more 45 degrees with respect to its upright pose will be counted as knock-down event. 
%---------------
\end{itemize}




\input{task/clear_table}
